Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on results

\Comment{ Several fuzzing methods
  have been proposed in the past, varying with respect to how new
  inputs are
  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}

Figure~\ref{fig:workflow} illustrates the 
differential testing infrastructure used in part of this study. It takes on
input a list of JS files and generates warnings on output. Boxes in
the figure denote encapsulation, arrowed lines denote data flow, and
the cycle icons denote repetition--the leftmost icon indicates that
each file in the input list will be analyzed in separate whereas the
rightmost icon shows that a single file will be fuzzed multiple times.
The bug-finding process works as follows. New inputs are obtained for
a given test input using some off-the-shelf input
fuzzer~\cite{fuzz-testing-history}; Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
The oracle checks whether or not the output produced for the fuzzed
file is consistent across all engines. In case the test passes in all
engines or fails in all engines (\ie{}, the output is consistent), the
infrastructure ignores the input. Otherwise, it considers the input as
potentially fault-revealing; hence, interesting for human
inspection. The infrastructure uses the
open-source tool eshost-cli~\cite{eshost-cli}, also used at
Microsoft, for checking output discrepancy.

@@

It is worth noting that a number of reasons exist, other than a bug,
to explain discrepancy (see Tables~\ref{fig:piecharts-transplantation}
and ~\ref{tab:false-positives}) and there is no clear automatic
approach to precisely distinguish false and true positives. As such, a
human needs to inspect the warning to classify the issue. To
facilitate inspection, we prioritized warnings and clustered them in
groups. We describe these strategies in the following.

@@

We classified warnings in two types, reflecting their likelihood of
manifesting a real bug. Warnings of the kind ``\hi{}'' are associated
with the cases where the test code executed to completion without
violating any internal checks, but it violated assertions declared in
the test itself or its harness. The rationale is that the input is
more likely to be valid as it it did not raise exceptions during the
execution of the application code, but, it manifested discrepancy
through the violation of an assertion declared in the test. In
contrast, warnings of type ``\lo{}'' are more likely to be asssociated
with invalid inputs. They reflect the cases where the anomaly is
observed during the execution of functions, which are part of the
application. We found that different engines often check
pre-conditions of those functions differently. It can happen, for
example, that one engine enforces a weaker pre-condition on a function
input compared to another engine and that is acceptable.\Comment{ For
  instance, it is acceptable to pass values greater than \Fix{x} to
  function \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those
cases, the infrastructure would observe a discrepancy that is more
likely to be associated with an invalid input produced by the fuzzer,
\ie{}, it is likely to be a ``bug'' in the test code as opposed to a
bug in the engine code. However, as expected, our heuristic is not
precise---``\lo'' warnings can reveal
bugs. Figure~\ref{fig:lo-truepositive} shows one of these cases. In
this example, the test instantiates an \CodeIn{ArrayBuffer} object and
stores an 8-bit integer at the 0 position. According to the
specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
exception should be thrown if a negative value is passed to the
function \CodeIn{ToIndex}, indirectly called by the test case. In this
case, however, the \chakra{} engine did not throw any exception. This
is a case of undocumented precondition, which is handled as a bug. It
was fixed by \chakra\ developers and is no longer present in the most
recent release of \chakra. Despite that case, most bugs we found
emerged from ``\hi{}'' warnings.

@@

Clusterization helps to group tests that fail for similar reasons. We
only clustered ``\lo'' warnings as ``\hi'' warnings produce messages
that arise from the test case, which are typically
distinct. Figure~\ref{fig:lo-truepositive} shows, at the bottom, the
error messages produced by a ``\lo'' warning. Any warning, including
this one, that has this same message signature will be included in the
same ``bucket''. To maximize the hit ratio we remove references to
code that may appear in the error messages.

@@

Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
1. RangeError: Offset is outside the bounds of the DataView
2. RangeError: byteOffset cannot be negative
3. RangeError: invalid or out-of-range index
  \end{lstlisting}
  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
    that led to a confirmed bug report in \chakra. The bug is caused
    by a required precondition check in the implementation of function
    \CodeIn{ToIndex} indirectly called by the test. }
\end{figure}

@@

%% This suggests that the investiment in
%% testing paid off in this case.
\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 2 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 217 & 106 & - & 278 \\
    Duktape & 0 & 4 & 4 & 1   \\
    \jerry{} & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\ 
   Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

\sloppy
\vspace{1ex}\noindent\textbf{Bug \# \Fix{6}.} The JS code \CodeIn{\{var a =
  \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}} manifested a bug in the \js{} engine \chakra{}.
The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the Radamsa fuzzer~\cite{radamsa}
returns a string representation of a null character (\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}",
used in the assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
  chakra did that it would be fine, no?} evaluates the unary
plus to NaN as expected, as the null character cannot be converted. As
result, the test fails as expected. \chakra{}, in contrast,
incorrectly converts the string to zero, making the test to pass. All
other engines fail on this test. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

>>>>

Figure~\ref{fig:workflow} illustrates the infrastructure for
differential testing, which is used in part of this study. It takes on
input a list of JS files and generates warnings on output. Boxes in
the figure denote encapsulation, arrowed lines denote data flow, and
the cycle icons denote repetition--the leftmost icon indicates that
each file in the input list will be analyzed in separate whereas the
rightmost icon shows that a single file will be fuzzed multiple times.
The bug-finding process works as follows. New inputs are obtained for
a given test input using some off-the-shelf input
fuzzer~\cite{fuzz-testing-history}.\Comment{ Several fuzzing methods
  have been proposed in the past, varying with respect to how new
  inputs are
  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
The oracle checks whether or not the output produced for the fuzzed
file is consistent across all engines. In case the test passes in all
engines or fails in all engines (\ie{}, the output is consistent), the
infrastructure discards the test. Otherwise, it considers the input as
potentially fault-revealing; hence interesting for human
inspection. The infrastructure uses the
open-source tool eshost-cli~\cite{eshost-cli}, also used at
Microsoft, for checking output discrepancy.

@@

Note that a number of reasons exist, other than a bug, to explain
discrepancy (see Table~\ref{tab:false-positives}) and there is no
clear way to distinguish false and true positives automatically. As
such, a human needs to inspect the warning to classify the issue. To
facilitate inspection, we prioritized warnings and clustered them in
groups. We describe these strategies in the following.

@@

We classified warnings in two types,
reflecting their likelihood of manifesting a real bug. Warnings of the
kind ``\hi{}'' are associated with the cases where the test code
executed to completion without violating any internal checks, but it
violated assertions declared in the test itself or its harness. The
rationale is that the input is more likely to be valid as it it did
not raise exceptions during the execution of the application code,
but, it manifested discrepancy through the violation of an assertion
declared in the test. In contrast, warnings of type ``\lo{}'' are
more likely to be asssociated with invalid inputs. They reflect the
cases where the anomaly is observed during the execution of functions,
which are part of the application. We found that different engines
often check pre-conditions of those functions differently. It can
happen, for example, that one engine enforces a weaker pre-condition
on a function input compared to another engine and that is
acceptable.\Comment{ For instance, it is acceptable to pass values greater than
\Fix{x} to function \CodeIn{\Fix{WWW}} in \Fix{y} but not in
\Fix{z}.} In those cases, the infrastructure would observe a
discrepancy that is more likely to be associated with an invalid input
produced by the fuzzer, \ie{}, it is likely to be a bug in the test
code not the engine (library or runtime) code. However, as expected, our heuristic
is not precise---``\lo'' warnings can 
reveal bugs. Figure~\ref{fig:lo-truepositive} shows one of these
cases. In this example, the test instantiates an \CodeIn{ArrayBuffer}
object and stores an 8-bit integer at the 0 position. According to the
specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
exception should be thrown if a negative value is passed to the
function \CodeIn{ToIndex}, indirectly called by the test case. In this
case, however, the \chakra{} engine did not throw any exception, which
violates the spec. This case of undocumented precondition, reported
and handled by developers as a bug, was fixed by developers after our bug
report and is no longer present in the most recent release of
\chakra. Despite that case, most bugs we found emerged from
``\hi{}'' warnings.

@@

Clusterization helps to group tests that fail for similar reasons. We
only clustered ``\lo'' warnings as ``\hi'' warnings produce messages
that arise from the test case, which are typically
distinct. Figure~\ref{fig:lo-truepositive} shows, at the bottom, the
error messages produced by a ``\lo'' warning. Any warning, including
this one, that has this same message signature will be included in the
same cluster, which we may also refer as a ``bucket''.

@@

Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
1. RangeError: Offset is outside the bounds of the DataView
2. RangeError: byteOffset cannot be negative
3. RangeError: invalid or out-of-range index
  \end{lstlisting}
  \caption{\label{fig:lo-truepositive}True positive example of a ``\lo''
    warning.}
\end{figure}

@@

%% This suggests that the investiment in
%% testing paid off in this case.
\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 2 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 279 \\
    Duktape & 0 & 4 & 4 & 1   \\
    \jerry{} & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\ 
   Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

\sloppy
\vspace{1ex}\noindent\textbf{Bug \#4} The JS code \CodeIn{\{var a =
  \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}} manifested a bug in the \js{} engine \chakra{}.
The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the Radamsa fuzzer~\cite{radamsa}
returns a string representation of a null character (\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}",
used in the assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
  chakra did that it would be fine, no?} evaluates the unary
plus to NaN as expected, as the null character cannot be converted. As
result, the test fails as expected. \chakra{}, in contrast,
incorrectly converts the string to zero, making the test to pass. All
other engines fail on this test. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

### 2018-08-25 paper/table_differential.tex
pass on results

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
    \midrule
%    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
%    \midrule    
    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
    & 2 & \textbf{\lo} & \jsc{} \\ 
    2  & 4/12 & radamsa & \chakra{}   & Rejected  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
    & - & \hi{} & \jsc{} \\
    3  & 4/14 & radamsa & \jsc{}  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & -  & \hi{} & \jsc{}    \\
    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
    & 2 & \hi{} & \jerry{}   \\
    5  & 4/29 & radamsa & \jsc{}  & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & 2  & \hi{}  & \jerry{}\\

@@

    \midrule
    \multirow{2}{*}{17} & \multirow{2}{*}{8/24}  &
    \multirow{2}{*}{quickfuzz} & \chakra{} & New &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}
    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
    & & & 
    \jsc{} & New &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}}
    & - &  & \\
   \bottomrule
  \end{tabular}
\end{table*}

>>>>

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
    \midrule
%    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
%    \midrule    
    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
    & 2 & \textbf{\lo} & \jsc{} \\ 
    2  & 4/12 & radamsa & \chakra{}   & WontFix  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
    & - & \hi{} & \jsc{} \\
    3  & 4/14 & radamsa & \jsc{}  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & -  & \hi{} & \jsc{}    \\
    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
    & 2 & \hi{} & \jerry{}   \\
    5  & 4/29 & radamsa & \jsc{}  & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & 2  & \hi{}  & \jerry{}\\

@@

    \midrule
    \multirow{2}{*}{17} & \multirow{2}{*}{8/24}  &
    \multirow{2}{*}{quickfuzz} & \chakra{} & New &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}
    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
    & & & 
    \jsc{} & New &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}}
    & - &  & \\
    \midrule
    18 & 8/24 & quickfuzz & \jsc{}  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=188930}{\#188930}}
    & - & \hi{} & Test262\\
   \bottomrule
  \end{tabular}
\end{table*}
